An Open Repository of Real-Time COVID-19 Indicators

### 2021-12-15 indicators/paper/paper.tex
Fix typo
Fix indicator paper typos

Altogether, we produce over 170 signals from 12 distinct sources, and provide
them in a common format foc access. This unifies both unique (unavailable
anywhere else) and standard COVID data streams into a single common 
format, enabling efficient comparison and modeling. A summary of the data
sources and signals in the API is in Table~\ref{tab:sources_signals}, and
detailed documentation is available online at
\url{https://cmu-delphi.github.io/delphi-epidata/api/covidcast_signals.html}.

@@

As an illustration, Figure~\ref{fig:vaccine-intent-compare} illustrates how CTIS
results in January 2021, based on an item asking survey respondents whether they
would accept a COVID-19 vaccine if one were vaccinated today, predicted actual
uptake of COVID-19 vaccines by July 2021 (as reported by the Centers for Disease
Control and Prevention). It also reveals a geographical disparity: in the
Northeast, actual vaccination rates more closely match vaccine willingness rates
in January than they do in the South, where vaccination rates lag overall. While 
these results must be interpreted carefully due to potential sampling biases in
the survey, they illustrate the potential of data in the COVIDcast API to inform
public health decision-making.

@@

There are a number of open questions, and challenges that remain. Several
signals are subject to biases, such as survey sampling and nonresponse biases,
geographic differences in market share for medical claims data, or biases in the
population represented in app-based mobility data.
% \cite{Coston:2021}. RJT: commenting out because if we cite only this, then I
% feel like we will have to provided references for the other sources of bias.
% Since otherwise it might look like we don't think there's credible work on the
% others.
Claims data tends also to be subject to biases during major national holidays
and other events that change health-seeking behavior. Characterizing these
biases will be important for future research and operational systems that use
these signals.  Several data sources are also subject to extensive revision and
backfill, which must be studied and modeled to enable effective real-time use of
these sources in forecasting and nowcasting systems. The breadth and unique
features of the COVIDcast API will help facilitate this and other related work,
which will be vital to advancing pandemic modeling and preparedness.

>>>>

Altogether, we produce over 170 signals from 12 distinct sources, and provide
them in a common format for access. This unifies both unique (unavailable
anywhere else) and standard COVID data streams into a single common 
format, enabling efficient comparison and modeling. A summary of the data
sources and signals in the API is in Table~\ref{tab:sources_signals}, and
detailed documentation is available online at
\url{https://cmu-delphi.github.io/delphi-epidata/api/covidcast_signals.html}.

@@

As an illustration, Figure~\ref{fig:vaccine-intent-compare} illustrates how CTIS
results in January 2021, based on an item asking survey respondents whether they
would accept a COVID-19 vaccine if one were offered today, predicted actual
uptake of COVID-19 vaccines by July 2021 (as reported by the Centers for Disease
Control and Prevention). It also reveals a geographical disparity: in the
Northeast, actual vaccination rates more closely match vaccine willingness rates
in January than they do in the South, where vaccination rates lag overall. While 
these results must be interpreted carefully due to potential sampling biases in
the survey, they illustrate the potential of data in the COVIDcast API to inform
public health decision-making.

@@

There are a number of open questions, and challenges that remain. Several
signals are subject to biases, such as survey sampling and nonresponse biases,
geographic differences in market share for medical claims data, or biases in the
population represented in app-based mobility data.
% \cite{Coston:2021}. RJT: commenting out because if we cite only this, then I
% feel like we will have to provided references for the other sources of bias.
% Since otherwise it might look like we don't think there's credible work on the
% others.
Claims data tends also to be subject to biases during major national holidays
and other events that change healthcare-seeking behavior. Characterizing these
biases will be important for future research and operational systems that use
these signals.  Several data sources are also subject to extensive revision and
backfill, which must be studied and modeled to enable effective real-time use of
these sources in forecasting and nowcasting systems. The breadth and unique
features of the COVIDcast API will help facilitate this and other related work,
which will be vital to advancing pandemic modeling and preparedness.
